Datasheet for 'Toronto Beaches Observations Dataset

### 2024-12-03 other/datasheet/datasheet.qmd
Fix references.
Fix some errors.

---
title: "Datasheet for 'Toronto Beaches Observations Dataset'"
subtitle: "A comprehensive dataset for analyzing environmental, temporal, and spatial factors affecting waterfowl counts on Toronto beaches"
author: 
  - Yizhe Chen
thanks: "Code and data are available at:[https://github.com/YizheChenUT/Waterfowl-on-Toronto-Beaches.git](https://github.com/YizheChenUT/Waterfowl-on-Toronto-Beaches.git)."
date: today
date-format: long
abstract: "The Toronto Beaches Observations Dataset is designed to analyze environmental, temporal, and spatial factors influencing waterfowl counts across Toronto beaches. It contains rich features including weather variables, water clarity, and seasonal indicators, enabling robust ecological and environmental modeling."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets.

>>>>

---
title: "Datasheet for 'Toronto Beaches Observations Dataset'"
subtitle: "A comprehensive dataset for analyzing environmental, temporal, and spatial factors affecting waterfowl counts on Toronto beaches"
author: 
  - Yizhe Chen
thanks: "Code and data are available at: [https://github.com/YizheChenUT/Waterfowl-on-Toronto-Beaches.git](https://github.com/YizheChenUT/Waterfowl-on-Toronto-Beaches.git)."
date: today
date-format: long
abstract: "The Toronto Beaches Observations Dataset is designed to analyze environmental, temporal, and spatial factors influencing waterfowl counts across Toronto beaches. It contains rich features including weather variables, water clarity, and seasonal indicators, enabling robust ecological and environmental modeling."
format: pdf
number-sections: true
bibliography: references.bib
---

Extract of the questions from @gebru2021datasheets. Some information are from @opendata.
